\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\setlength{\parindent}{0pt}

\title{EECE7065 --- Project Report 1}
\author{\
		Wayne Stegner
		\and
		Zuguang Liu
		\and
		Siddharth Barve
}
\date{\vspace{-36pt}}

\begin{document}
		\maketitle

		\par Our project is studying the penguin colony’s social thermoregulation
		as an emergent swarm behavior.
		Our progress thus far include relevant literature review, preliminary
		design simulation, making decisions as well as constructing the base
		framework for the final design.
		Through literature study, we have learned some general biological facts
		about the penguin colony, but have not found similar research that
		addresses the self-emergent aspect of the behavior.
		After implementing a preliminary design based on general thermodynamic
		rules, we were able to observe huddling behavior in the penguins to
		regulate body temperature in the cold environment.
		However, we found that implementing features, such as collision detection
		and a better heat transfer model, on a continuous space is quite
		challenging.
		Thus, we decided to discretely place penguin entities in a discrete grid of
		tessellating shapes, starting with square as a solution easiest to
		implement.
		We then started to build the environment framework for this solution.
		Our future plan is to enhance the framework we have established as well as
		specify different policies for the penguin agents.
		Eventually, we will put together the final design and hopefully be able to
		simulate the colony to be as realistic as possible.
		Some specific areas we hope to investigate in the swarm behavior include
		the effect of different decision making models, the effect of taking away
		certain senses, the radius of the senses, environmental changes, and the
		ability to evolve the decision models.

\end{document}
